04_DESeq_sexes

### 2019-05-29 analysis/01_limma_all.Rmd
rename
umm, two days old commits

```{r}
library(limma)
library(Glimma)
library(edgeR)
library(kableExtra)
library(cowplot)

knitr::opts_chunk$set(fig.path = '../figures/',cache=TRUE)

@@

```{r read}
# import "colData" which contains sample information and "countData" which contains read counts
colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
head(colData)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
```

@@

>>>>

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("Glimma")

library(limma)
library(Glimma)
library(edgeR)
library(kableExtra)
library(cowplot)

knitr::opts_chunk$set(fig.path = '../figures/01_limma/',cache=TRUE)

@@

```{r read}
# import "colData" which contains sample information and "countData" which contains read counts
colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
head(colData)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

@@

```{r newRplot}

myMDSplot <- plotMDS(parentalobject, cex = 0.5)

names(myMDSplot$x)
names(myMDSplot$y)

mergedMDS <- data.frame(myMDSplot$x, myMDSplot$y)

head(mergedMDS)

names(mergedMDS) <- c("x", "y", "par", "treatment", "rep", "tissue")
mds_GC_final_merged <- ggplot(mergedMDS, aes(x, y)) + 
  geom_point(aes(color = treatment, shape = rep)) + 
  geom_rug(aes(colour = treatment)) + 
  facet_grid(par ~ tissue) + 
  labs(title = "ggplot of GC new ref samples") + 
  theme(strip.text.x = element_text(size = 8))
mds_GC_final_merged
```

### 2019-05-29 analysis/04_DESeq2_sexes.Rmd
umm, two days old commits

```{r plotpca, eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels

```
```{r pca, eval = T}
mylegend <- get_legend(p1)

@@

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()
```

>>>>

```{r pca, eval=T}
p1 <- plotPC1(pcas.female_hypothalamus, "female hypothalamus", "26% PC1 variance explained") 
p2 <- plotPC1(pcas.female_pituitary, "female pituitary", "11% PC1 variance explained")   
p3 <- plotPC1(pcas.female_gonad, "female gonad", "37% PC1 variance explained") 
p4 <- plotPC1(pcas.male_hypothalamus, "male hypothalamus", "28% PC1 variance explained") 
p5 <- plotPC1(pcas.male_pituitary, "male pituitary" , "11% PC1 variance explained") 
p6 <- plotPC1(pcas.male_gondad, "male gonad", "14% PC1 variance explained") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels

mylegend <- get_legend(p1)

@@

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 14)
plot(pc1)
dev.off()

p11 <- plotPC1(pcas.female_hypothalamus, "female hypothalamus", "26% PC1 variance explained") 
p12 <- plotPC1(pcas.female_pituitary, "female pituitary", "11% PC1 variance explained")   
p13 <- plotPC1(pcas.female_gonad, "female gonad", "37% PC1 variance explained") 
p14 <- plotPC1(pcas.male_hypothalamus, "male hypothalamus", "28% PC1 variance explained") 
p15 <- plotPC1(pcas.male_pituitary, "male pituitary" , "11% PC1 variance explained") 
p16 <- plotPC1(pcas.male_gondad, "male gonad", "14% PC1 variance explained") 
p11 + theme_noaxislabels
p12 + theme_noaxislabels
p13 + theme_noaxislabels
p14 + theme_noaxislabels
p15 + theme_noaxislabels
p16 + theme_noaxislabels

allPC12 <- plot_grid(p1 + theme_noaxislabels + ylim(c(-35,35)), 
                     p4 + theme_noaxislabels + ylim(c(-35,35)), 
                     p2 + theme_noaxislabels + ylim(c(-35,35)),
                     p5 + theme_noaxislabels + ylim(c(-35,35)),
                     p3 + theme_nolegend + ylim(c(-35,35)) ,
                     p6 + theme_nolegend + ylim(c(-35,35)) ,
                     ncol = 2)

pc12 <- plot_grid(allPC12, mylegend,  nrow = 2, rel_heights = c(1.0, 0.15))
pc12

pdf("../figures/sexes/pca-12.pdf", width = 12, height = 14)
plot(pc12)
dev.off()
